Manuscript figures

### 2024-11-26 Manuscript_figures.Rmd
Updated R manuscript figures R Markdown and report

@@

    # Wilcoxon
    stat.test <- plot.dat %>%
      group_by(bin, sex) %>%
      wilcox_test(mm~sex_visit, paired = F)

@@

# Wilcoxon
stat.test <- plot.dat %>%
  group_by(bin, sex) %>%
  wilcox_test(value~sex_visit, paired = F)

@@

# Plot
ggplot(plot.dat, aes(bin, value)) + 
  geom_boxplot(aes(fill = sex_visit), position = position_dodge(), outlier.shape = NA) +
  geom_point(aes(fill = sex_visit), position = position_jitterdodge(jitter.width = 0.1), 
             color = "black", size = 0.5, alpha = 0.2) +
  theme_bw() +
  labs(x = "", y = "Normalized pseudobulk expression", fill = "", title = "C3") +
  theme(line = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        axis.text = element_text(color = "black")) +
  scale_fill_manual(values = c(colorRampPalette(c("pink","darkred"))(3), colorRampPalette(c("lightblue","blue3"))(3))) +
  geom_text(inherit.aes = F, data = sex.stat, aes(ct, y = 1.5e3, label = sig, group = sex), position = position_dodge(width = 0.9)) + # KW
  stat_pvalue_manual(stat.test, label = "p.adj.signif", tip.length = 0.01, bracket.nudge.y = 0.2, hide.ns = F) # Wilcoxon
```

@@

## Figure S3H-J

@@

>>>>

# Wilcoxon
stat.test <- plot.dat %>%
  group_by(anno, sex) %>%
  wilcox_test(value~sex_visit, paired = T) %>% 
  mutate(., p.adj.signif = apply(., 1, \(x) if(x[10] > 0.05 && x[10] <= 0.1) "." else x[11])) %>% 
  filter(p.adj.signif != "ns", !is.na(p)) %>% # Remove those not significant for KW
  add_xy_position(x = "anno", dodge = 0.8, scales = "free_y", fun = "mean_sd", step.increase = 0.05)

@@

    # Wilcoxon
    stat.test <- plot.dat %>%
      group_by(bin, sex) %>%
      wilcox_test(mm~sex_visit, paired = T)

@@

# Wilcoxon
stat.test <- plot.dat %>%
  group_by(bin, sex) %>%
  wilcox_test(value~sex_visit, paired = T)

@@

# Plot
ggplot(plot.dat, aes(bin, value)) + 
  geom_boxplot(aes(fill = sex_visit), position = position_dodge(), outlier.shape = NA) +
  geom_point(aes(fill = sex_visit), position = position_jitterdodge(jitter.width = 0.1), 
             color = "black", size = 0.5, alpha = 0.2) +
  theme_bw() +
  labs(x = "", y = "Normalized pseudobulk expression", fill = "", title = "C3") +
  theme(line = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        axis.text = element_text(color = "black")) +
  scale_fill_manual(values = c(colorRampPalette(c("pink","darkred"))(3), colorRampPalette(c("lightblue","blue3"))(3))) +
  geom_text(inherit.aes = F, data = sex.stat, aes(ct, y = 1.5e3, label = sig, group = sex), position = position_dodge(width = 0.9)) + # KW
  stat_pvalue_manual(stat.test, label = "p.adj.signif", tip.length = 0.01, bracket.nudge.y = 0.2, hide.ns = F)# Wilcoxon
```

@@

## Figure S3H-J,L

@@

Load data for S3H-J first
